---
title: "Check on 29th data"
author: "Raymond R Balise"
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2:
    df_print: kable
    number_sections: false
    toc: true
    config:
      toc:
        collapse: 2
    toc_depth: 4
    toc_float: true
    
    theme: default
    highlight: tango 
---

```{r setup}
library(conflicted)
suppressMessages(conflict_prefer("filter", "dplyr"))
suppressPackageStartupMessages(library(tidyverse))

library(haven)
library(compareDF)
```

```{r}


oldFile  <- "covid-19 abril 27.dta"
newFile <- "covid-19 mayo 01 v2.dta"

  old <- read_stata(paste0("../data/", oldFile), encoding = "latin1")
  new <- read_stata(paste0("../data/", newFile), encoding = "latin1")
```
  
# Variables with diffeent names
```{r}
# https://bookdown.org/Maxine/r4ds/comparing-two-data-frames-tibbles.html
  dplyr::all_equal(old, new)
```
  
## Fixing names of variables  
```{r fixNames}  
newRenamed <- new %>% 
  rename(`Icu_beds` = `Icubeds`)
```

# Check variable attributes
```{r checkAttributes}
  dplyr::all_equal(old, newRenamed)
```

## Details on attribute discrepancies
Variable names/labels have changed and the numeric percision has changed.

```{r attributeDifs}

  checkAttrs <- function(oldVar, newVar) {
    cat(paste0("Old: ", as.list(match.call(expand.dots=FALSE)))[[2]], "\n")
    cat("Attributes:\n")
    print(attributes(oldVar))
    #print(x)
    cat("\n")
    
    cat(paste0("New: ", as.list(match.call(expand.dots=FALSE)))[[3]], "\n")
    cat("Attributes:\n")
    x <- attributes(newVar)
    print(x)
    cat("\n")
    }
  
  checkAttrs(old$Hospital_Beds, newRenamed$Hospital_Beds)
  checkAttrs(old$Hospital_Beds_Per_Capita, newRenamed$Hospital_Beds_Per_Capita)
  checkAttrs(old$Icu_beds, newRenamed$Icu_beds)
  checkAttrs(old$Icubeds_Per_Capita, newRenamed$Icubeds_Per_Capita)
  checkAttrs(old$Population, newRenamed$Population)
  checkAttrs(old$GDP_Rank, newRenamed$GDP_Rank)
  checkAttrs(old$Marginalization_Rank, newRenamed$Marginalization_Rank)
  checkAttrs(old$cases_per_capita, newRenamed$cases_per_capita)
  checkAttrs(old$deaths_per_capita, newRenamed$deaths_per_capita)
  checkAttrs(old$deaths_per_cuci, newRenamed$deaths_per_cuci)
  checkAttrs(old$pop2, newRenamed$pop2)
  checkAttrs(old$rank_daily, newRenamed$rank_daily)
  
```

## Erase attributes and check again
```{r}
old[] <- lapply(old, function(x) { attributes(x) <- NULL; x })
newRenamed[] <- lapply(newRenamed, function(x) { attributes(x) <- NULL; x })

dplyr::all_equal(old, newRenamed)
```

# Subset the new data to have only the old dates (same number of rows)
```{r}
oldDays <- max(old$Days)

oldShouldMatch <- old %>%  
    arrange(State_Code, Days ) %>% 
    mutate(StateNameDays = paste0(State_Name, "~", Days))

newShouldMatch <- newRenamed %>% 
  filter(Days <= oldDays) %>% 
  arrange(State_Code, Days ) %>% 
  mutate(StateNameDays = paste0(State_Name, "~", Days))

#theDiffs <- dplyr::all_equal(oldShouldMatch, newShouldMatch)

```

# Identify the first 100 different records
```{r varDiffs}
varDiffs <- compareDF::compare_df(oldShouldMatch, newShouldMatch, c("StateNameDays"))
create_output_table(varDiffs, limit = 100)
```

The population estimates are now more percise.

# Identify first 1000 differences ignoring population 
There are many additional changes to the old data.

```{r varDiffsWithoutPop}
cutOldShouldMatch <- 
  oldShouldMatch %>% 
  select(-Population)

cutNewShouldMatch <- 
  newShouldMatch %>% 
  select(-Population)

cutVarDiffs <- compareDF::compare_df(cutOldShouldMatch, cutNewShouldMatch, c("StateNameDays"))
create_output_table(cutVarDiffs, limit = 1000)
```


